### 2014-03-26 ms_probaweb.tex
Some edits, first sentence of the intro

\begin{itemize}
\item The community is more than a species list. Interactions are central. \\

\item Network structure do vary in space in time. \\

@@

The niche concept is key to understand and predict species
distribution. Several attempts have been made to refresh it, but its main
usage still follows Hutchinson’s idea that species interactions restrict
the fundamental niche to a realized one \parencite{Blonder2014}. Despite its
intuitive interpretation and translation into species distribution models,
the concept has been constantly criticized (Hardin, 1960; Peters, 1991;
Chase2003; Silvertown, 2004; Soberon, 2007) and several attempts have been
made to expand and reinforce it.

Part of the problem surrounding the definition of the niche has been clarified
with the distinction between Eltonian and Grinnellian definitions (ChaseLeibold
2003). The Grinnellian dimension of the niche is the effect of the environment
on the demography of a species, while the Eltonian dimension is the effect of a
species on its environment sensu lato. The Grinnellian niche is the most
intuitive one to apply and is the conceptual backbone of species distribution
models. The Eltonian niche is well known by food web ecologists, but it is much
more difficult to formulate into distribution models. Nonetheless, the
development of the niche model of food web structure (Williams2000) and its parameterization (Williams2010; Gravel2013) made
it more operational.

While it is straigthforward to represent statistically the hyper volume where a species
occurs, it is much more challenging to account for ecological interactions.
Chase and Leibold (2003) attempted this representation in their definition:
\textit{[The niche is] the joint description of the environmental conditions
that allow a species to satisfy its minimum requirements so that the birth rate
of a local population is equal or greater than its death rate along with the set
of per capita effects of that species on these environmental conditions.} They
represented the niche graphically with zero-net growth isoclines (the Grinnelian
niche) and impact vectors (the Eltonian niche). While this representation has
been very influential in community ecology at the local scale, it remains
unpracticable at the biogeographical one. The absence of any mathematical
representation of the niche that could easily be fit to ecological data perhaps
explain why biogeographers are still struggling to develop species distribution
models taking into account ecological interactions.

>>>>

Most ecology textbooks define the ecological community at \quote{the pool of
species occupying a given location at a given time, and the list of their
interactions} (ref to Morin?). Yet we oft forget the last part of this
definition, focusing on species and neglecting the way they interact.

\begin{itemize}
\item Network structure do vary in space in time. \\

@@

The niche concept is key to understand and predict species
distribution. Several attempts have been made to refresh it, but its main
usage still follows Hutchinson’s idea that species interactions restrict
the fundamental niche to a realized one, and ecologists haven't moved far past
the n-dimensional hypervolume formalism \parencite{Blonder2014}. Despite its
intuitive interpretation and translation into species distribution models,
the concept has been constantly criticized (Hardin, 1960; Peters, 1991;
Chase2003; Silvertown, 2004; Soberon, 2007) and several attempts have been
made to expand and reinforce it.

Part of the problem surrounding the definition of the niche has been
clarified with the distinction between Eltonian and Grinnellian definitions
(ChaseLeibold 2003). The Grinnellian dimension of the niche is the effect of
the environment on the demography of a species, while the Eltonian dimension
is the effect of a species on its environment \emph{sensu lato}.  % SNOB!
The Grinnellian niche is the most intuitive one to apply and is the conceptual
backbone of species distribution models. The Eltonian niche is well known
by community ecologists, but is trickier to turn into predictive models
\parencite{Devictor2010a}. Nonetheless, the development of the niche model
of food web structure (Williams2000) and its parameterization (Williams2010;
Gravel2013) made it more operational, although it has yet to be applied to
more than trophic interactions. %Y'a pas que les food webs dans la vie!

While it is straigthforward to represent statistically the hyper volume where a species
occurs, it is much more challenging to account for ecological interactions.
Chase and Leibold (2003) attempted this representation in their definition:
\textit{[The niche is] the joint description of the environmental conditions
that allow a species to satisfy its minimum requirements so that the birth rate
of a local population is equal or greater than its death rate along with the set
of per capita effects of that species on these environmental conditions.} They
represented the niche graphically with zero-net growth isoclines (the Grinnelian
niche) and impact vectors (the Eltonian niche). While this representation has
been very influential in community ecology at the local scale, it remains
unpracticable at the biogeographical one.
% Why (or more to the point, what do we care about having the same definition at different scales?)?
The absence of any mathematical
representation of the niche that could easily be fit to ecological data perhaps
explain why biogeographers are still struggling to develop species distribution
models taking into account ecological interactions.
